%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Amirali Iranmanesh} \\ \vspace{1pt}
    \small +49-157-392-83240 $|$ \href{mailto:airanmanes@constructor.university}{\underline{airanmanes@constructor.university}} $|$ 
    \href{https://www.linkedin.com/in/amirali-iranmanesh/}{\underline{linkedin.com/in/amirali-iranmanesh}} $|$
    \href{https://github.com/aircode610}{\underline{github.com/aircode610}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Constructor University}{Bremen, Germany}
      {Bachelor of Science in Software, Data and Technology}{Sept. 2024 -- May 2027}
      \resumeItemListStart
        \resumeItem{Awarded the competitive JetBrains Full Scholarship (2024–2027).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Research Intern}{June 2025 -- Aug. 2025}
      {JetBrains, Education Research Team}{Berlin, Germany}
      \resumeItemListStart
        \resumeItem{Refactored KOALA plugin to improve modularity, readability, and maintainability.}
        \resumeItem{Developed server-side UI with Spring Boot, integrating JSON-based config management and unit tests with JUnit.}
        \resumeItem{Dockerized backend services and migrated local configs to AWS S3 for automated generation.}
        \resumeItem{Added KOALA plugin features for granular, privacy-aware data tracking to improve precision and flexibility.}
        \resumeItem{Collaborated on research tasks, contributed to workshop material, and produced a project demo video.}
    \resumeItemListEnd
    
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Teaching Assistant, Scientific Programming with Python}{Sept. 2025 -- Present}
      {Constructor University}{Bremen, Germany}
      \resumeItemListStart
        \resumeItem{Developed auto-graded GitHub Classroom assignments and mentored students in debugging.}
        \resumeItem{Prepared exercises in scientific computing topics, including NumPy, pandas, and Matplotlib.}
        \resumeItem{Held seminars to mentor students and reinforce key programming concepts.}
    \resumeItemListEnd

    \resumeSubheading
      {Research Assistant, Stabilizing Structures}{June 2023 -- Sept. 2023}
      {Shahid Bahonar University of Kerman}{Kerman, Iran}
      \resumeItemListStart
        \resumeItem{Modeled earthquake-resistant arcs by applying trigonometry and physics to lateral force simulations.}
        \resumeItem{Developed Python algorithms with NumPy and Matplotlib, adding Excel and graphs to enhance usability.}
    \resumeItem{Mentored peers in programming, enabling collaborative debugging and research contributions.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Smart Assess — Exam Analysis Platform} $|$ \emph{Python, Flask, Google Gemini API, PyPDF2, Jinja2}}{2025}
          \resumeItemListStart
            \resumeItem{Built a Flask-based web app for professors to upload exams, manage keys, and analyze results.}
            \resumeItem{Integrated Google Gemini Vision API for OCR and implemented error-pattern clustering with PDF highlighting.}
            \resumeItem{Generated detailed per-student and class reports with automated workflows for actionable feedback.}
          \resumeItemListEnd
        
      \resumeProjectHeading
          {\textbf{Gene Knowledge Web Service} $|$ \emph{Python, Flask, Plotly, Pandas, NumPy, LangChain, OpenAI API}}{2025}
          \resumeItemListStart
            \resumeItem{Built an interactive Flask-based platform to analyze protein activity differences in aging research.}
            \resumeItem{Developed volcano plots, boxplots, and responsive UI with Plotly for dynamic visualization.}
            \resumeItem{Integrated PubMed APIs and AI-enhanced gene summaries using LangChain and OpenAI.}
          \resumeItemListEnd
        
        \resumeProjectHeading
          {\textbf{BreakpointTracker — IntelliJ Plugin} $|$ \emph{Kotlin, IntelliJ Platform SDK, Gradle}}{2025}
          \resumeItemListStart
            \resumeItem{Developed an IntelliJ plugin to track and list breakpoints in real-time within a custom tool window.}
            \resumeItem{Supported multiple breakpoint types with seamless IDE integration.}
            \resumeItem{Implemented efficient navigation and packaged with Gradle for deployment on IntelliJ IDEA.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

\section{Awards \& Achievements}
 \resumeSubHeadingListStart
   \resumeItem{Placed in the top 1\% of students nationwide in Iran.}
   \resumeItem{Top 15\% in International Olympiad in Informatics (IOI) – First Round.}
   \resumeItem{Perfect SAT Math score (800) with a total SAT score of 1480.}
   \resumeItem{Ranked 1st in Code Up's C++ Programming Contest and Animation branch of Visual Programming Competition.}
 \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Kotlin, C, C++, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: Spring Boot, Django, Flask, FastAPI, Bootstrap} \\
     \textbf{Developer Tools}{: Git, Docker, AWS S3, IntelliJ IDEA, PyCharm, VS Code, Jupyter} \\
     \textbf{Testing \& CI/CD}{: JUnit, PyTest, Gradle, GitHub Actions} \\

     \textbf{Libraries}{: NumPy, Pandas, Matplotlib, Plotly, LangChain/LangGraph, scikit-learn} 
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
